---
title: "Approximation of the Distribution in R Markdown"
author: "Linda1103"
date: "2020/3/24"
output:
  html_document: default
  pdf_document:
    latex_engine: xelatex
fontsize: 12pt
keywords: Monte Carlo methods,R Markdown,bookdown
documentclass: article
papersize: letter
abstract: The report represent the approximation of the distribution function of $N(0,1)$ by the Monte Carlo methods.In addition,it involes how to input math fomulas ,form the table and draw theplots by R Markdown and bookdown.
---

# 1 Introduction

  As we all know,correctly writting basic syntax of R Markdown is the key of finishing report.Therefore,I studyed some skills from & laquo A Data Science Lab Project Template in R Markdown & laquo.
  The rest of report includes three sections as follow:math equations,experiment results and conclusions.
  

# 2 Math equations

  approximation of the distribution function of  N(0,1)
\begin（equation）
$$\Phi(t)=\int_{-\infty}^t\frac{1}{\sqrt{2\pi}}{\rm e}^{\frac{-y^2}{2}}\,{\rm d}y$$
\label{eq：N（0,1）}
\end{equation}
Monte Carlo methods:
\begin（equation）
$$\hat\Phi(t)={\frac{1}{n}}\sum_{i=1}^{n}I({X_i}\leq t),$$
\label{eq:Monte Carlo methods}
\end{equation}
## Where $X_i$ are a random sample from $N（0,1）$and $I()$ is the indicator function.

# 3 Experiment results

  I carryied out the experiment with  the approximation at $n\in{\{10^2,10^3,10^4}\}$ at $t\in{\{0.0,0.67,0.84,1.28,1.65,2.32,2.58,3.09,3.72}\}$ to form a table.In addition,The table include the true value for comparison.The specific experiment procedure code is as follow.

```{r norm,echo = T }
n=c(100,1000,10000)
t=c(0.0,0.67,0.84,1.28,1.65,2.32,2.58,3.09,3.72 )
p=matrix(data=NA,nrow=3,ncol=9)
#填充矩阵元素
#a=0
for(i in 1:3)
  for(j in 1:9)
   for (k in 1:100) {
     #a=a+1
     num=rnorm(n[i],mean=0,sd=1)#行元素服从高斯分布
     p[i,j]=mean(num<t[j])
     #print(a)
  }
rownames(p)<-n#改变矩阵行名
colnames(p)<-t
pcycle=array(0,dim=c(9,3,100))
#真实值
true_value<-c(pnorm(0),pnorm(0.67),pnorm(0.84),pnorm(1.28),pnorm(1.65),
           pnorm(2.32),pnorm(2.58),pnorm(3.09),pnorm(3.72))
p<-rbind(p,true_value)#合并P和true_value两行
p<-round(p,digits=9)

library(knitr)
library(magrittr)
library(kableExtra)
kable(p, booktabs=TRUE, caption='(norm_table)') %>%
  kable_styling("responsive",full_width = F,fixed_thead = T) %>% 
  row_spec(0,bold=T,color="blue")
  
 
```
 
   In addition, I repeat the experiment 100 times. Draw box plots of the 100 approximation errors at each $t$  using ggplot2 for each $n$.I just finished this part according below codes.

```{r repeat norm,echo=T}                  
t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
x=pnorm(t, mean = 0, sd = 1)
n1=100
z=matrix(0,100,9)
w=matrix(0,9,n1)
for(p in 1:100)
{ y=c(rnorm(n1,mean=0,sd=1))
  for(k in 1:9)
   {
   for(j in 1:n1)
   {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n1}}
z=as.data.frame(z)
e100_1=z$V1-x[1]
e100_2=z$V2-x[2]
e100_3=z$V3-x[3]
e100_4=z$V4-x[4]
e100_5=z$V5-x[5]
e100_6=z$V6-x[6]
e100_7=z$V7-x[7]
e100_8=z$V8-x[8]
e100_9=z$V9-x[9]

t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
x=pnorm(t, mean = 0, sd = 1)
n2=10^3
z=matrix(0,100,9)
w=matrix(0,9,n2)
for(p in 1:100)
{ y=c(rnorm(n2,mean=0,sd=1))
  for(k in 1:9)
  {
   for(j in 1:n2)
  {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n2}}
z=as.data.frame(z)
e1000_1=z$V1-x[1]
e1000_2=z$V2-x[2]
e1000_3=z$V3-x[3]
e1000_4=z$V4-x[4]
e1000_5=z$V5-x[5]
e1000_6=z$V6-x[6]
e1000_7=z$V7-x[7]
e1000_8=z$V8-x[8]
e1000_9=z$V9-x[9]

t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
x=pnorm(t, mean = 0, sd = 1)
n3=10000
z=matrix(0,100,9)
w=matrix(0,9,n3)
for(p in 1:100)
{ y=c(rnorm(n3,mean=0,sd=1))
  for(k in 1:9)
   {
   for(j in 1:n3)
   {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n3}}
z=as.data.frame(z)
e10000_1=z$V1-x[1]
e10000_2=z$V2-x[2]
e10000_3=z$V3-x[3]
e10000_4=z$V4-x[4]
e10000_5=z$V5-x[5]
e10000_6=z$V6-x[6]
e10000_7=z$V7-x[7]
e10000_8=z$V8-x[8]
e10000_9=z$V9-x[9]

plot_data=cbind.data.frame(e100_1,e100_2,e100_3,e100_4,e100_5,e100_6,e100_7,e100_8,e100_9,e1000_1,e1000_2,e1000_3,e1000_4,e1000_5,e1000_6,e1000_7,e1000_8,e1000_9,e10000_1,e10000_2,e10000_3,e10000_4,e10000_5,e10000_6,e10000_7,e10000_8,e10000_9)
```

```{r draw box plots,echo=T }
library(ggplot2)
library(lattice)
library(plyr)
library(Rmisc)
plot1<-ggplot(data=plot_data,aes(y=e100_1,x="0-100"))+geom_boxplot()+
    labs(title="Boxplot of error at t=0, n=100",y="error",
         x=NULL)
plot1

plot2<-ggplot(data=plot_data,aes(y=e100_2,x="0.67-100"))+geom_boxplot()+
    labs(title="Boxplot of error at t=0.67, n=100",y="error",
         x=NULL)
plot2

plot3<-ggplot(data=plot_data,aes(y=e100_3,x="0.84-100"))+geom_boxplot()+
    labs(title="Boxplot of error at t=0.84, n=100",y="error",
         x=NULL)
plot3

plot4<-ggplot(data=plot_data,aes(y=e100_4,x="1.28-100"))+geom_boxplot()+
    labs(title="Boxplot of error at t=1.28, n=100",y="error",
         x=NULL)
plot4

plot5<-ggplot(data=plot_data,aes(y=e100_5,x="1.65-100"))+geom_boxplot()+
    labs(title="Boxplot of error at t=1.65, n=100",y="error",
         x=NULL)
plot5

plot6<-ggplot(data=plot_data,aes(y=e100_6,x="2.32-100"))+geom_boxplot()+
    labs(title="Boxplot of error at t=2.32, n=100",y="error",
         x=NULL)
plot6

plot7<-ggplot(data=plot_data,aes(y=e100_7,x="2.58-100"))+geom_boxplot()+
    labs(title="Boxplot of error at t=2.58, n=100",y="error",
         x=NULL)
plot7

plot8<-ggplot(data=plot_data,aes(y=e100_8,x="3.09-100"))+geom_boxplot()+
    labs(title="Boxplot of error at t=3.09, n=100",y="error",
         x=NULL)
plot8

plot9<-ggplot(data=plot_data,aes(y=e100_9,x="3.72-100"))+geom_boxplot()+
    labs(title="Boxplot of error at t=3.72, n=100",y="error",
         x=NULL)
plot9

```

# 4 Conclusions

   In a word,I inputted two formulars and created a table to describe the difference between approximation and true value.In addition,I drew box plots of the 100 approximation errors at each $t$  using ggplot2 for each $n$.And I found the error is decreasing as the number of samples become larger.Anyway,In this homework,I received a lot of knowledge and I will make persistent efforts.
